
\section*{\DIFdelbegin \DIFdel{Abbreviations}\DIFdelend \DIFaddbegin \DIFadd{List of abbreviations}\DIFaddend }
  MRI: magnetic resonance imaging; NFBS: Neurofeedback Skull-stripped; CSF: cerebrospinal fluid; BEaST: brain extraction based on nonlocal segmentation technique; BET: brain extraction technique; HWA: hybrid watershed technique; IBSR: Internet brain segmentation repository; LPBA40: LONI Probabilistic Brain Atlas; ADNI: Alzheimer's Disease Neuroimaging Initiative\DIFaddbegin \DIFadd{; UCLA: University of California, Los Angeles; NKI: Nathan Kline Institute
  }\DIFaddend 

\DIFaddbegin \section*{\DIFadd{Ethics approval and consent to participate}}

\DIFadd{All experimental procedures were performed with approval of the Nathan S. Kline Institute for Psychiatric Research institutional review board and only after informed consent was obtained.
}

\section*{\DIFadd{Consent for publication}}

\DIFadd{All participants consented to have their data shared.
}


\DIFaddend \section*{Competing interests}
  The authors declare that they have no competing interests.

\section*{\DIFdelbegin \DIFdel{Author's contributions}%DIFDELCMD < }
%DIFDELCMD <     %%%
\DIFdel{RCC}\DIFdelend \DIFaddbegin \DIFadd{Funding}}
\DIFadd{This work was supported by R01MH101555 from the National Institute of Mental Health to RCC.
}


\section*{\DIFadd{Authors' contributions}}
    \DIFadd{RCC }\DIFaddend designed the Neurofeedback study and Skull-stripped repository;  BP and EST performed manual correction and validation of results; BP performed the validation analyses; BP, RCC, JSP, and JPP wrote the data note. All authors read and approved of the final version.

\section*{Acknowledgements}
  We would like to thank Dr. Simon Fristed Eskildsen for help with the installation and optimization of the BEaST method. We would also like to acknowledge Qingyang Li for creating the BEaST guide, as well as the Bash script that we based our script on. Lastly, we would like to thank all of those involved in the participation, data collection, and data sharing initiative of the Enhanced Rockland Sample.
  \DIFdelbegin \DIFdel{This work was supported by R01MH101555 from the National Institute of Mental Health to RCC.
 }\DIFdelend \DIFaddbegin 

%DIF > \section*{Endnotes}

\theendnotes
 \DIFaddend