\documentclass{article}

\usepackage{lipsum}
% \usepackage{layout}

\newcommand{\ts}{\textsuperscript}
%\usepackage{fontspec}
%\setmainfont{Calibri}
\providecommand\CMItoname{}
\providecommand\CMItoaddress{}
\providecommand\CMItoopeningname{Editor}
\providecommand\CMIreline{Data note submission to GigaScience Brainhack Thematic Series}
\input{NKIletterdefs}

\begin{document}
\sffamily

I am writing to submit our manuscript entitled ``The Preprocessed Connectomes Project Repository of Manually-Corrected Skull-Stripped T1-Weighted Anatomical MRI Data'' for consideration to be published in GigaScience as a Data note in the Brainhack Thematic Series - Open Tools for Neuroscience.

Consistent with the ethos of Brainhack, our paper describes a contribution of manual effort to add value to the data shared through the NKI Enhanced Rockland Sample Neurofeedback project (NFB). The T1 weighted structural MRI data from the project were skull-stripped using a semi-automatic method, in which the results of the state-of-the-art BEaST algorithm were carefully manually corrected. The resulting data can be used by researchers to improve the quality of preprocessing of the NFB data and as gold sample data to train and validate new skull-stripping algorithms. The BEaST skull-stripping library generated can be used to improve the automatic processing of future NFB releases and other datasets. As such, we believe that the described repository will be useful to a variety of neuroscience and image processing researchers.

The data note describes the data and the procedures used to generate the skull-stripped data. The data were validated by close visual inspection by multiple raters. We illustrate the value of the repository by using it to compare different automatic brain extraction algorithms. 

I am an editor of this thematic series and request that it be handled by one of the other editors. Other than this, I and my other authors have no competing interest. All authors have approved the manuscript for submission. The content of this manuscript has been submitted to bioR$\chi$iv but has not been published in any other outlet.

We greatly appreciate your consideration of this manuscript and look forward to your response.


\end{document}
